\documentclass[11pt,a4paper,sans]{moderncv}

\moderncvstyle{casual}
\moderncvcolor{blue}

\usepackage[utf8]{inputenc}
\usepackage[scale=0.75]{geometry}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{atbegshi}
\usepackage[unicode]{hyperref}

% --- GitHired watermark (subtle bottom-right stamp) ---

% -------------------------------------------------------

\name{Alex}{Doe}
\title{Data Scientist — Machine Learning & Analytics}
\address{123 Example Street}{10000 Example City}{Country}
\phone[mobile]{+00 000 000 0000}
\email{alex.doe@example.com}

\begin{document}

\recipient{To: Hiring Team}{TechCorp International\\
Amsterdam, Netherlands}
\date{\today}
\opening{Dear Hiring Team,}
\closing{Kind regards,}

\makelettertitle

I am writing to express my enthusiasm for the position of \textit{Data Scientist — Machine Learning \& Analytics} at TechCorp International. With a background in applied physics and hands-on experience developing predictive models and data pipelines, I am eager to contribute to data-driven innovation within your global analytics team.

In my recent role, I built and maintained Python-based ETL workflows and deployed machine learning models that improved forecasting accuracy and automated reporting. I collaborated closely with cross-functional stakeholders to translate analytical insights into practical strategies, emphasizing code quality, documentation, and reproducibility. These practices reflect the same principles of reliability and transparency that TechCorp applies across its technology ecosystem.

What excites me most about this role is the opportunity to bridge technical depth with creative problem-solving. I am passionate about crafting interpretable models, optimizing performance under production constraints, and mentoring teams toward scalable, maintainable solutions. TechCorp’s focus on responsible AI development and open collaboration aligns perfectly with my professional philosophy.

I would welcome the chance to discuss how my skills in data engineering, modeling, and process optimization could support TechCorp’s analytics initiatives. Thank you for considering my application.

\makeletterclosing

\end{document}
