\documentclass[11pt,a4paper,sans]{moderncv}
\nopagenumbers{}
\moderncvcolor{blue}
\moderncvstyle{banking}

% ------------------------------------------------------------
% Essentials only
% ------------------------------------------------------------
\usepackage[scale=0.75]{geometry}
\usepackage{fontawesome5}
\usepackage{xcolor}
\usepackage[unicode]{hyperref}
\usepackage{pagecolor}
\usepackage{tikz}
\usepackage{atbegshi}

% ------------------------------------------------------------
% Colors & background
% ------------------------------------------------------------
\definecolor{customcolor}{HTML}{8DD9BF}
\definecolor{mybackground}{HTML}{84848A}

\pagecolor{mybackground}
\color{white}
\definecolor{white}{RGB}{255,255,255}
\colorlet{color0}{white}

\hypersetup{
  colorlinks=true,
  linkcolor=customcolor,
  urlcolor=customcolor,
  citecolor=customcolor
}

% ------------------------------------------------------------
% Subtle watermark
% ------------------------------------------------------------


% ------------------------------------------------------------
% Personal Info (anonymized)
% ------------------------------------------------------------
\name{\textcolor{white}{Alex}}{\textcolor{white}{Doe}}
\email{alex.doe@example.com}
\phone[mobile]{+00 000 000 0000}
\social[linkedin]{alexdoe}
\social[github]{alexdoe-dev}
\extrainfo{\faYoutube\ \href{https://www.youtube.com/@ExampleChannel}{ExampleChannel}}

% ------------------------------------------------------------
% Document Body
% ------------------------------------------------------------
\begin{document}

\makecvtitle

\section{Summary}
Data and AI engineer with a background in applied physics, specializing in retrieval-augmented generation (RAG), large language models, and backend automation. Experienced in building scalable APIs, orchestrating data pipelines, and integrating modern AI tooling with clean, reproducible engineering workflows.

\section{Skills}
\cvitem{\textcolor{black}{AI/LLM \& RAG}}{OpenAI API, LangChain, RAG design (chunking, embeddings, retrieval), Pinecone, Pydantic I/O, prompt chaining, fallback logic}
\cvitem{\textcolor{black}{Backend \& APIs}}{Python, Flask, FastAPI, REST, Swagger, SQLAlchemy}
\cvitem{\textcolor{black}{Frontend}}{React, Vite, TailwindCSS, shadcn/ui}
\cvitem{\textcolor{black}{Data \& ML}}{Pandas, NumPy, scikit-learn, TensorFlow, Matplotlib}
\cvitem{\textcolor{black}{Ops \& Tooling}}{Docker, GitHub Actions, LangSmith, Postman, SQLite, PostgreSQL, Pytest, Git, \LaTeX}

\section{Experience}
\cventry{2024--Present}{\textcolor{black}{Data Engineer / AI Developer}}{\textcolor{black}{TechSolutions Inc.}}{}{}{}{
\begin{itemize}
  \item Designed Python ETL pipelines for structured/unstructured data ingestion.
  \item Integrated OpenAI-powered endpoints with FastAPI; deployed via Docker and CI/CD.
  \item Improved reproducibility and observability through strict logging and documentation.
\end{itemize}}

\cventry{2022--2024}{\textcolor{black}{Freelance Developer (AI \& Automation)}}{\textcolor{black}{Global Clients}}{}{}{}{
\begin{itemize}
  \item Built full-stack AI apps using Flask/React, RAG pipelines, and automated reporting dashboards.
  \item Delivered technical writing, LaTeX document automation, and reproducible scientific workflows.
\end{itemize}}

\cventry{2020--2022}{\textcolor{black}{Research Assistant}}{\textcolor{black}{University of Example}}{}{}{}{
\begin{itemize}
  \item Conducted computational modeling in Python and C++; implemented symbolic algebra routines.
  \item Collaborated on simulation pipelines for physics-based models; validated results analytically.
\end{itemize}}

\section{Projects}
\cvitem{\textcolor{black}{RAG Chat Assistant}}{\href{https://github.com/example/RAG-Chat}{\textbf{Document Chat System}} — Flask backend + React UI, document ingestion pipeline with embeddings and contextual responses. Dockerized and observable via LangSmith.}
\cvitem{\textcolor{black}{README Generator}}{\href{https://github.com/example/readmegen}{\textbf{AI README Generator}} — Flask API + React UI, ranks repo files for inclusion and produces structured README drafts.}
\cvitem{\textcolor{black}{LinkedIn Icebreaker}}{\href{https://github.com/example/icebreaker-agent}{\textbf{LLM-based Networking Tool}} — Agent pipeline that scrapes LinkedIn and crafts personalized messages.}
\cvitem{\textcolor{black}{Tax AI App}}{\href{https://github.com/example/tax-ai}{\textbf{AI-driven Tax Assistant}} — Flask + React app offering natural language tax insights, with automated CI builds.}

\section{Education}

\cventry
  {2021}
  {\textcolor{black}{M.Sc. in Data Science}}
  {\textcolor{black}{University of Example}}
  {}
  {}
  {Thesis: \href{https://example.com/thesis.pdf}{\textit{Data-driven Modeling for Predictive Analytics}} \\
   GPA: 8.7/10}

\cventry
  {2018}
  {\textcolor{black}{B.Sc. in Physics}}
  {\textcolor{black}{University of Example}}
  {}
  {}
  {GPA: 7.1/10}


\section{Other Highlights}
\cvitem{\textcolor{black}{YouTube}}{\textcolor{red}{\faYoutube}\ \href{https://www.youtube.com/@ExampleChannel}{ExampleChannel} — Educational videos on data, AI, and scientific computing.}
\cvitem{\textcolor{black}{2023}}{Speaker, Data \& AI Meetup — “Prompt Engineering for Transparent Workflows.”}
\cvitem{\textcolor{black}{2022}}{Workshop Organizer, “Building Practical LLM Apps with Python.”}
\cvitem{\textcolor{black}{2019–20}}{Technical Writer, \href{https://examplemagazine.com}{Example Magazine}.}

\end{document}
